Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2021-07-12 minimax.tex
Table Two Phases 20 runs + display names and URL

\author{Submission 15}
\institute{}

%\author{Beatrice Napolitano\inst{1}\orcidID{0000-0002-3887-6206} \and
%Olivier Cailloux\inst{1}\and
%Paolo Viappiani\inst{2}}
%%
%\authorrunning{B. Napolitano et al.}
%% First names are abbreviated in the running head.
%% If there are more than two authors, 'et al.' is used.
%%
%\institute{Université Paris-Dauphine, Université PSL, CNRS, LAMSADE \and
%LIP6, UMR 7606, CNRS and Sorbonne Universit\'e \\
%\email{beatrice.napolitano@dauphine.fr}}

\maketitle              % typeset the header of the contribution
\vspace{4em}
%
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in
%150--250 words.
\begin{sloppypar}
Social choice deals with the problem of determining a consensus choice from the preferences of different agents. In the classical setting, the voting rule is fixed beforehand and full information concerning the preferences of the agents is provided. This assumption of full preference information has recently been questioned by a number of researchers and several methods for eliciting the preferences of the agents have been proposed. In this paper we argue that in many situations one should consider as well the voting rule to be partially specified. Focusing on positional scoring rules, we assume that the chair, while not able to give a precise definition of the rule, is capable of answering simple questions requiring to pick a winner from a concrete profile. In addition, we assume that the agent preferences also have to be elicited. We propose a method for robust approximate winner determination and interactive elicitation based on minimax regret; we develop several strategies for choosing the questions to ask to the chair and the agents in order to converge quickly to a near-optimal alternative. Finally, we analyze these strategies in experiments where the rule and the preferences are simultaneously elicited.
\end{sloppypar}
\keywords{Uncertainty in AI \and Computational Social Choice \and Preference Elicitation.}
\end{abstract}
%
%
%
\section{Introduction}
Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
In many situations, such as in group recommender systems, the goal is to find a consensus choice;
social choice theory can provide foundations for such applications.
%The traditional approach to social choice assumes that both the social choice function and the full preference orderings of the agents (agents) are expressed beforehand. These represent two strong hypothesis.
The traditional approach to social choice assumes that 1) the full preference orderings of the agents and 2) the social choice function are expressed beforehand. These represent two strong hypotheses.
Requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost).
This observation has motivated several works assuming partial preference orders: 
%and incremental elicitation of agent preferences. 
%In the context of social choice, several authors have been interested in obtaining information about winners with reduced assumptions about the knowledge of the agent preferences (assuming that the voting rule is known).
one early work is  by Conitzer and Sandholm \cite{Conitzer2005} who studied the complexity of communication when using different voting rules; %determining lower and upper bounds;
%they showed that, 
%in the worst case, the agents should send their complete set of preference for several rules. 
Konczak and Lang \cite{Konczak05} studied the computation of possible and necessary winners for various voting rules; %and showed that the problem is hard in the general case.
Xia and Conitzer \cite{Xia2008} then showed that, while the identification of a necessary co-winner in scoring rules is polynomial,  the determination of possible co-winners is NP-hard;
% they also  proposed polynomial-time algorithms when using maximin and Bucklin.
additional complexity results were given by Walsh \cite{Walsh2007} and Pini et al. \cite{Pini2007}.
%\cite{Walsh2007} showed that the general case remains computationally hard even when restricting to single-peaked preferences;  sufficient conditions that ensure tractability were then found \cite{Pini2007}.

@@

			0	&	0.62	&	0.52	&	0.62	&	0.52	\\
			15	&	0.515	&	0.48	&	0.54	&	0.46	\\
			30	&	0.345	&	0.47	&	0.325	&	0.425	\\
			50	&	0.045	&	0.09	&	0.03	&	0.065	\\
			100	&	0.14	&	0.23	&	0.075	&	0.135	\\
			200	&	2.305	&	1.36	&	2.145	&	1.845	\\
			300	&	5.15	&	2.38	&	6.83	&	0.625	\\
			400	&	10.905	&	0.89	&	12.245	&	0.99	\\
			500	&	20.0	&	0.0	&	20.0	&	0.0	\\

@@

As part of our contribution, an open-source library, to reproduce our experiments and perform many more, will be made publicly available. (URL not displayed for reasons of anonymity.)
%and serve as a basis for further research

>>>>

%\author{Submission 15}
%\institute{}

\author{Beatrice Napolitano\inst{1}\orcidID{0000-0002-3887-6206} \and
Olivier Cailloux\inst{1}\and
Paolo Viappiani\inst{2}}
%
\authorrunning{B. Napolitano et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Université Paris-Dauphine, Université PSL, CNRS, LAMSADE \and
LIP6, UMR 7606, CNRS and Sorbonne Universit\'e \\
\email{beatrice.napolitano@dauphine.fr}}

\maketitle              % typeset the header of the contribution
%
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in
%150--250 words.
\begin{sloppypar}
Social choice deals with the problem of determining a consensus choice from the preferences of different agents. In the classical setting, the voting rule is fixed beforehand and full information concerning the preferences of the agents is provided. This assumption of full preference information has recently been questioned by a number of researchers and several methods for eliciting the preferences of the agents have been proposed. In this paper we argue that in many situations one should consider as well the voting rule to be partially specified. Focusing on positional scoring rules, we assume that the chair, while not able to give a precise definition of the rule, is capable of answering simple questions requiring to pick a winner from a concrete profile. In addition, we assume that the agent preferences also have to be elicited. We propose a method for robust approximate winner determination and interactive elicitation based on minimax regret; we develop several strategies for choosing the questions to ask to the chair and the agents in order to converge quickly to a near-optimal alternative. Finally, we analyze these strategies in experiments where the rule and the preferences are simultaneously elicited.
\end{sloppypar}
\keywords{Uncertainty in AI \and Computational Social Choice \and Preference Elicitation.}
\end{abstract}
%
%
%
\section{Introduction}
Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
In many situations, such as in group recommender systems, the goal is to find a consensus choice;
social choice theory can provide foundations for such applications.
%The traditional approach to social choice assumes that both the social choice function and the full preference orderings of the agents (agents) are expressed beforehand. These represent two strong hypothesis.
The traditional approach to social choice assumes that 1) the full preference orderings of the agents and 2) the social choice function are expressed beforehand. These represent two strong hypotheses.
Requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost).
This observation has motivated several works assuming partial preference orders: 
%and incremental elicitation of agent preferences. 
%In the context of social choice, several authors have been interested in obtaining information about winners with reduced assumptions about the knowledge of the agent preferences (assuming that the voting rule is known).
one early work is  by Conitzer and Sandholm \cite{Conitzer2005} who studied the complexity of communication when using different voting rules; %determining lower and upper bounds;
%they showed that, 
%in the worst case, the agents should send their complete set of preference for several rules. 
Konczak and Lang \cite{Konczak05} studied the computation of possible and necessary winners for various voting rules; %and showed that the problem is hard in the general case.
Xia and Conitzer \cite{Xia2008} then showed that, while the identification of a necessary co-winner in scoring rules is polynomial,  the determination of possible co-winners is NP-hard;
% they also  proposed polynomial-time algorithms when using maximin and Bucklin.
additional complexity results were given by Walsh \cite{Walsh2007} and Pini et al. \cite{Pini2007}.
%\cite{Walsh2007} showed that the general case remains computationally hard even when restricting to single-peaked preferences;  sufficient conditions that ensure tractability were then found \cite{Pini2007}.

@@

			0	&	0.59	&	0.59	&	0.59	&	0.59	\\
			15	&	0.5		&	0.49	&	0.55	&	0.58	\\
			30	&	0.32	&	0.45	&	0.36	&	0.46	\\
			50	&	0.08	&	0.2 	&	0.14	&	0.27	\\
			100	&	0.39	&	0.57	&	0.23	&	0.46	\\
			200	&	2.13	&	1.59	&	2.38	&	1.23	\\
			300	&	5.8 	&	1.65	&	6.65	&	1.46	\\
			400	&	11.28	&	1.09	&	11.94	&	1.22	\\
			500	&	20.0	&	0.0	&	20.0	&	0.0	\\

@@

As part of our contribution, we provide an open-source library \url{https://github.com/oliviercailloux/minimax}, to reproduce our experiments and perform many more.
%will be made publicly available.(URL not displayed for reasons of anonymity.)
%and serve as a basis for further research
